Greenhouse gas emissions model - making scenarios

### 2021-11-12 Scenarios_report.Rmd
now extracting milk yield, live weight, weight gain and feeding system from survey table. Digestable energy and crude protein are also extracted, but just as averages per farm for now. Uncertainty analysis now shown per head.

variables_to_update<-c(paste0("N_animal_type_",1:12),"feeding_system","feed_prod_CO2","feed_trans_CO2")

scenarios<-data.frame(Variable=variables_to_update,param="both")

@@

@@

for (f in Farms)
  {coln<-paste0("Farm_",f)
   scenarios[which(scenarios$Variable %in% "feeding_system"),coln]<-
     median(Kenyaherds[which(Kenyaherds$QQNO==f),"system"])
   scenarios[which(scenarios$Variable %in% "feed_prod_CO2"),coln]<-
     median(Kenyaherds[which(Kenyaherds$QQNO==f),"feed_kgCO2"])
   scenarios[which(scenarios$Variable %in% "feed_trans_CO2"),coln]<-
     median(Kenyaherds[which(Kenyaherds$QQNO==f),"feed.transport_kgCO2"])

@@

# Uncertainty

@@

```{r name_in_out_vars}
in_var  <- GHG_simulation_scenarios$y$milk_yield # "Total Milk Yield"
out_var <- GHG_simulation_scenarios$y$on_farm # "Total emissions"
```

>>>>

variables_to_update_const<-c(paste0("N_animal_type_",1:12),
                             "feeding_system")

scenarios<-data.frame(Variable=variables_to_update_const,param="both")

variables_to_update_posnorm<-c(paste0("milk_yield_",4:6),
                             "feed_prod_CO2",
                             "feed_trans_CO2",
                             paste0("live_weight_LW_",1:12),
                             paste0("weight_gain_WG_",1:12),
                             "DE_perc",
                             "perc_crude_protein_diet")

scenarios<-rbind(scenarios,data.frame(Variable=rep(variables_to_update_posnorm,each=3),param=c("lower","upper","distribution")))

@@

### error estimates for variables
milk_yield_error<-0.25
feed_trans_error<-0.25
feed_prod_error<-0.25
live_weight_error<-0.1
weight_gain_error<-0.1
digestible_energy_error<-0.1
crude_protein_error<-0.1

@@

for (f in Farms)
  {coln<-paste0("Farm_",f)
  # update feeding system 
  scenarios[which(scenarios$Variable == "feeding_system"),coln]<-
     median(Kenyaherds[which(Kenyaherds$QQNO==f),"system"])

  # update digestible energy (mean for all animals for now) (with error)
  scenarios[which(scenarios$Variable == "DE_perc"),coln][1:2]<-
     mean(Kenyaherds[which(Kenyaherds$QQNO==f),"dig_energy"])*
                           c(1-digestible_energy_error,1+digestible_energy_error)

  # update crude protein (mean for all animals for now) (with error)
  scenarios[which(scenarios$Variable == "perc_crude_protein_diet"),coln][1:2]<-
     mean(Kenyaherds[which(Kenyaherds$QQNO==f),"CP."])*
                           c(1-crude_protein_error,1+crude_protein_error)

  # update feed production CO2 (with error)
   scenarios[which(scenarios$Variable == "feed_prod_CO2"),coln][1:2]<-
     mean(Kenyaherds[which(Kenyaherds$QQNO==f),"feed_kgCO2"])*
                           c(1-feed_prod_error,1+feed_prod_error)
  # update feed transport CO2 (with error)
   scenarios[which(scenarios$Variable == "feed_trans_CO2"),coln][1:2]<-
     mean(Kenyaherds[which(Kenyaherds$QQNO==f),"feed.transport_kgCO2"])*
                           c(1-feed_trans_error,1+feed_trans_error)
  # update milk yield for each cow type (animal type 4-6) (with error)
   for(typ in 4:6)
     if(sum(Kenyaherds$QQNO==f&Kenyaherds$animal_type==typ)>0)
       scenarios[which(scenarios$Variable==paste0("milk_yield_",typ)),coln][1:2]<-
         mean(Kenyaherds[which(Kenyaherds$QQNO==f&Kenyaherds$animal_type==typ),
                         "milk_yield"])*c(1-milk_yield_error,1+milk_yield_error)
  # update live weight and weight gain for each animal type (with error)
   for(typ in 1:12)
     if(sum(Kenyaherds$QQNO==f&Kenyaherds$animal_type==typ)>0)
       {scenarios[which(scenarios$Variable==paste0("live_weight_LW_",typ)),coln][1:2]<-
         mean(Kenyaherds[which(Kenyaherds$QQNO==f&Kenyaherds$animal_type==typ),
                         "live_weight_LW"])*c(1-live_weight_error,1+live_weight_error)
       scenarios[which(scenarios$Variable==paste0("weight_gain_WG_",typ)),coln][1:2]<-
         mean(Kenyaherds[which(Kenyaherds$QQNO==f&Kenyaherds$animal_type==typ),
                         "weight_gain_WG"])*c(1-weight_gain_error,1+weight_gain_error)
     }

   for(varia in variables_to_update_posnorm)
   if(sum(is.na(scenarios[which(scenarios$Variable==varia),coln][1:2]))==0)   
     if(!equals(scenarios[which(scenarios$Variable==varia),coln][1],
               scenarios[which(scenarios$Variable==varia),coln][2]))
        scenarios[which(scenarios$Variable==varia&
                   scenarios$param=="distribution"),coln]<-"posnorm" else
            scenarios[which(scenarios$Variable==varia&
                   scenarios$param=="distribution"),coln]<-"const"

@@

# Normalizing milk yield and emissions per head

```{r}

animals_per_run<-rowSums(GHG_simulation_scenarios$x[paste0("N_animal_type_",1:12)])

milk_yield_per_head<-GHG_simulation_scenarios$y$milk_yield/animals_per_run
total_emissions_per_head<-GHG_simulation_scenarios$y$on_farm/animals_per_run

# Uncertainty for per-head data

@@

```{r name_in_out_vars}
in_var  <- milk_yield_per_head # "Total Milk Yield"
out_var <- total_emissions_per_head # "Total emissions"
```
